Progressive Second Price Auction Mechanism for Data-Exchange Models

### 2019-10-02 main.tex
Ty!

%\documentclass[master,tocprelim]{Latex/Classes/PhDthesisPSnPDF}
%\documentclass[letterpaper,12pt]{cls/thesis}
%\documentclass[master,final,tocprelim]{unrthesis}
\documentclass[master,tocprelim,12pt]{unrthesis}
%\documentclass[master,tocprelim,12pt]{thesis}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{float}
%\usepackage{wrapfig}
%\usepackage{showkeys}
\usepackage{algorithm2e}
\usepackage{plain}
\usepackage{pdfpages}

\usepackage{listings}

\graphicspath{{./graphics/}}

\lstset{ %
language=C,               
basicstyle=\footnotesize,
showspaces=false,               
showstringspaces=false,         
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=10pt,     
showtabs=false,                 
columns=fullflexible,
frame=single,          
tabsize=2,          
captionpos=b,       
extendedchars=true,
frame=single,
breaklines=true,       
breakatwhitespace=false, 
escapeinside={\%*}{*)}       
}
\def\verbatimtabsize{4\relax}
\def\listingoffset{1em}
\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{property}{Property}[chapter]

\title{Dynamical Systems: Chaotic Attractors and \\{~}
    Synchronization using Time-Averaged Partial \\{~}\\
\vskip-12pt
Observations of the Phase Space}
\author{
Jordan Fleming Blocher 
}

%\date{\today}

\newcommand{\cF}{{\mathcal F}}
\newcommand{\cO}{{\mathcal O}}
\newcommand{\cA}{{\mathcal A}}
\newcommand{\cB}{{\mathcal B}}
\newcommand{\cV}{{\mathcal V}}
%\newcommand{\R}{\textbf{R}}
\newcommand{\R}{{\bf R}}
\newcommand{\B}{{\cal B}}
\newcommand{\C}{\textbf{C}}
\newcommand{\del}{\delta}
\newcommand{\cL}{{\mathcal L}}
\newcommand{\mydelta}{{h}}
\newcommand{\yourdelta}{{\Delta}}
\def\words#1{\quad\hbox{#1}\quad}
\def\wwords#1{\qquad\hbox{#1}\qquad}
\renewcommand{\emptyset}{\O}
\numberwithin{equation}{chapter}
\begin{document}

\maketitle

\includepdf{ms-committee-page.pdf}

@@

We study the synchronization of chaotic systems when the coupling
between them contains both time averages and stochastic noise.
Our model dynamics are given by the Lorenz equations
which are a system of three ordinary differential
equations in the variables $X$, $Y$ and $Z$.
Our theoretical results show that coupling two copies of the
Lorenz equations using a feedback control which consists
of time averages of the $X$ variable
leads to exact synchronization provided the
time-averaging window is known and sufficiently small.
In the presence of noise the convergence is to within a
factor of the variance of the noise.
The novelty of our investigation hinges on the
analysis of the time averages.
We also consider the case when the time-averaging window
is not known and show that it is possible to tune the
feedback control to recover the size of the
time-averaging window.
Further numerical computations
show that synchronization is more accurate and occurs
under much less stringent conditions than our theory requires.

\end{abstract}

\begin{acknowledgements}
I would like to acknowledge my thesis advisor, Eric Olson.
I would like to thank my committee members:
Bruce Blackadar, Paul Hurtado and Fred Harris.
I would also like to thank my friends, family and UNR.
This research is supported in part by NSF grant DMS-1418928.
\end{acknowledgements}

\contentspage
\tablelistpage
\figurelistpage

\begin{manuscript}
\chapter{Introduction}\label{Intro}

We produce synchronization results when coupling is applied on 
two chaotic systems when the coupling
between them contains both time averages and stochastic noise.
Our model dynamics are given by the Lorenz equations
which are a system of three ordinary differential
equations in the variables $X$, $Y$ and $Z$.
We build off of investigations of the Lorenz model in 
\cite{Hayden11, Stuart14}, where 
space and continuous time observations \cite{Olson14} by use of a control
theory perspective similar to that which arises from the derivation of
continuous time limits of discrete time filters \cite{ Bloemker14}. 
We seek to determine relationships between the underlying
dynamical system and the observation operator
to ensure that synchronization can be obtained.
For a coupled pair of chaotic dynamical systems,
where the driven system's initialization is not known precisely, the extent 
of the use of observed data over time is a topic of interest in 
meteorology, weather forecasting and any attempt to predict the 
future using incomplete information about the current state of a
dynamical model.

In this thesis, we extend the approach of \cite{Olson14}
to use time-averaged continuous-in-time partial observations of 
the phase space. We examine
both the noise-free case and the case where the observations include
stochastic noise. We are able to show that the use of time-averaged
observations results in synchronization.
The techniques investigated here are applicable to different
dissipative dynamical systems, and
provide many points of continued study, which
are detailed in a chapter dedicated to future work.

The outline of the thesis is as follows. In Chapter 1 we introduce the concept
of synchronization on the global attractor. We also provide a
detailed description of our model problem, a simplified model of atmospheric
convection, the Lorenz system, and present an analytical bound on the
trajectories which is used throughout the thesis. We also introduce the coupling
method that is is the focus of the thesis and introduce the notation that will
be used to describe our experiments.
In Chapter 2 we present a proof of the
existence and uniqueness of our solution. In addition, we present a generalized
Gronwall integration proof that will be used throughout the thesis and is
applicable to the convergence of our model. 
In chapter three we study the convergence of the approximating solution in a noise-free 
setting, ending with an investigation into the sensitivity of the time-averaging
window. Chapter 4 presents an analysis when the observations contain stochastic noise. 
Chapters 5 and 6 present our numerical methods and conclusions. Finally, Chapter
7 provides points of future work.

\section{Synchronization}\label{Synchro}

Synchronization means that the difference between two solution
trajectories converge to zero as time tends to infinity.  The sensitivity
to initial conditions of dynamical systems means that two identical
systems with even a slight perturbation of initial conditions quickly
become uncorrelated even though they are bounded and converging to the
same attractor.  
On the theoretical side, we would like to determine 
when coupling between two identical copies of a dynamical system
leads to synchronization and to study the effects that
realistic conditions, such as a moving time-averages and 
noisy observations, have on the synchronization.
On the computational
side, we would like to simulate the same things and test the
sharpness of our theory.

Consider a dynamical system given by the ordinary differential equations
\begin{equation}\label{freeODE}
    \frac{dU}{dt} = \cF(U) 
\end{equation}
where $U(0) = U_0\in{\bf R}^n$ and ${\cal F}\colon{\bf R}^n\to{\bf R}^n$.
We use partial information about $U$ to drive a second solution $u$
as follows:
\begin{equation}\label{noerra}
    \frac{du}{dt} = \cF(u) + \mu\big(\widetilde{\cal R}(U) - {\cal R}(u)\big)
\end{equation}
with arbitrary initial condition $u(0) = u_0$.
Here $\widetilde{\cal R}(U)$ denotes an interpolation of
partial observations of $U$ back into the phase space ${\bf R}^n$
that may contain noise as well moving time averages, and
${\cal R}(u)$ denotes a feedback control used to nudge $u$
towards $U$ over time.
Note that the relaxation parameter $\mu > 0$ 
determines the rate
at which $u$ is nudged towards $U$ as it evolves forward in time 
and represents a tunable parameter in the system.

Note, we assume the forcing function ${\cal F}$ is known 
exactly and leads to a well posed dynamical system that governs
the freely evolving solution.
More realistically, ${\cal F}$ might only be known up to an
approximation $\widetilde {\cal F}$.  Ideas for work along these 
lines is discussed in Section \ref{whatissigma} in the
chapter on future work.  
We assume the dynamics given by ${\cal F}$ are dissipative.
However, our analysis relies not just on dissipativity, but
on a squeezing property with respect to the observable
part of the phase space.

If $\widetilde{\cal R}={\cal R}$ and $u_0=U_0$, then
$\mu\big((\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)= 0$.
It follows that both $u$ and $U$ evolve according to the same
dynamics, which in turn implies $u(t)=U(t)$ for all $t\ge 0$.
When $u_0\ne U_0$ it may still happen
%provided $\widetilde{\cal R}={\cal R}$ 
that $\|u(t)-U(t)\|\to 0$ as $t\to\infty$.
When this happens we say that $u$ synchronizes with $U$.
Note, however, when $\widetilde{\cal R}\ne{\cal R}$ it
may happen that
$\mu(\big(\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)\ne 0$
even if $U_0=u_0$.
It immediately follows that $U(t)\ne u(t)$ for $t>0$.
In this case, we look for bounds on $\|U-u\|$ that depend
on the quality of the approximation $\widetilde{\cal R}\approx{\cal R}$.

If the observations $\widetilde{\cal R}$ have been 
contaminated using a moving time average with a known window size,
then ${\cal R}$ can also include an identical moving time average
so that $\widetilde{\cal R}={\cal R}$.  However, if the size of
the averaging window is unknown, then we can only guess its size.
In this case ${\cal R}$ is only an approximation of $\widetilde{\cal R}$.
Similarly, if the observations $\widetilde{\cal R}$ contain a 
unknown noise term, this this noise can not be included in the 
feedback term and again ${\cal R}$ will differ from 
$\widetilde{\cal R}$, this time by the noise.
The main result of this thesis are theoretical and numerical
bounds on the expected value of $\|U-u\|^2$ in the case 
when $\widetilde{\cal R}$
contains noisy observations that have been averaged with
respect to an unknown window size.

\section{Global Attractors}

For general continuous time dynamical systems the number of degrees of freedom
is often associated with the number of first order ordinary differential
equations (ODEs) in the model.  If
$$ 
\displaystyle\sum_{i=1}^n{\partial \cF_i \over \partial U_i }< 0,
$$
then the system is said to be
\emph{dissipative} system.
This indicates that volumes transported by the dynamics of
the system are contracting.
In this case, there exists a compact set to which all bounded 
sets converge as they are transported by the flow.
In particular, all trajectories eventually converge that set.
Moreover, if this set is invariant, that is, if every point on
the attractor is the image under the flow of the
dynamics over a fixed period of time of another point on the attractor, 
then the set is unique and called the global attractor.
Since the attractor is bounded and invariant, then any trajectory 
on the attractor is bounded backwards in time.
This leads to another characterization of the attractor
as the set of all solutions which are bounded backwards
in time.  
Note that the set of fixed points such that 
$\big\{\, x : {\cal F}(x)=0 \,\big\}$ are included in the attractor,
as is the unstable manifold of the fixed point.
This observation can be used to find lower bounds on the
size of the attractor.

Due to the presence of an attractor, the sum of the Lyapunov
exponents is expected to be negative; an indication that the 
system is dissipative. 
The Lyapunov exponents control the exponential growth or
contraction of volume elements in phase space \cite{Doering95a}.
They 
quantify the exponential divergence of infinitesimally close 
state-space trajectories 
and estimate the amount of chaos in a system. 
A positive exponent is consistent with diagnosing chaos and represents
local instability in a particular direction.

The Lyapunov spectrum is represented geometrically as a small $n$-dimensional 
sphere of initial conditions.
%, where $n$ is the degrees of freedom in the system.
In a chaotic attractor, the sphere evolves into an ellipsoid whose
principal axes expand (or contract) at rates given by the Lyapunov
exponents.
Calculating the largest Lyapunov exponent can yield an estimate 
of the ``level of chaos" using the slope of the divergence
as was calculated by Rosenstein and Collins \cite{Rosenstein93}.
This determines how two trajectories with nearby initial conditions 
diverge over time.
In fact, we expect that two randomly chosen initial 
conditions in arbitrary phase space will diverge exponentially at 
the rate given by the largest Lyapunov exponent. 
In the context of the synchronization studies in this thesis, 
it is this tendency for the
trajectories to diverge that needs to be overcome by the
feedback controller represented by $\mu\big(\tilde{\cal R}(U)-{\cal R}(u)\big)$
in equation~(\ref{noerra}).

\section{The Lorenz '63 Model}

The Lorenz '63 Model is a system of three ordinary differential equations that
represent a simplified model of atmospheric convection \cite{Lorenz63}. 
The model is dissipative with a quadratic energy-conserving nonlinearity.
This system of three coupled non-linear ordinary differential
equations satisfies equation~(\ref{freeODE}) where
$U=(X,Y,Z)$ and
\begin{align}\label{freeLorenz}
    \cF(U)=\begin{bmatrix}\sigma(Y-X)\\
    -\sigma X-Y-XZ\\ -bZ+XY-b(r+\sigma)\end{bmatrix}.
\end{align}
Here $\sigma$ is
the Prandtl number, $r$ is the Rayleigh number, 
and $b$ is a geometric factor. 
Note that we have employed a coordinate system where 
the center is shifted to the point $(0, 0, 0)$.
We will use the standard parameter values 
$\sigma=10$, $b=8/3$ and $r=28$
in our study.  
At these values, the system is known to 
have a chaotic global attractor $\cA$, Tucker \cite{Tucker1999}.

Note that
$$
\displaystyle\sum_{i=1}^3{\partial \cF_i \over \partial U_i }
	=-\sigma-1-b
$$	
which shows the system is dissipative.
Moreover, linearization about the
fixed point $$(\sqrt{b(r-1)},\sqrt{b(r-1)},-\sigma-1)$$
gives the matrix
$$
\begin{bmatrix}
    -\sigma & \sigma & 0\\
    1 & -1 & -\sqrt{b(r-1)}\\
    \sqrt{b(r-1)} & \sqrt{b(r-1)} & -b
\end{bmatrix}.
$$
which has eigenvalues
\begin{align*}
	\lambda_1&\approx -13.85457791\\
\quad
	\lambda_2&\approx 0.093955624 - 10.19450522i\\
\quad
	\lambda_3&\approx 0.093955624 + 10.19450522i.
\end{align*}
Since the real parts of two of these eigenvalues is positive,
nearby solutions will
spiral away onto a two-dimensional unstable manifold. 
We conclude that the unstable manifold at the fixed point
is two dimensional.
Therefore, the global attractor contains a two dimensional
set and is itself at least two dimensional.

The Lorenz attractor has been shown to be a global 
attractor contained in a
volume bounded by a sphere, a cylinder, the volume between two parabolic sheets,
an ellipsoid and a cone \cite{Doering95a}, see
also \cite{Doering95b}.
A smaller sphere which also contains the attractor was 
discovered while attempting to improve estimates used in
the proof of Proposition~\ref{UKNLTAprop}.
While we did not make use of that bound in this thesis,
it has been included as Appendix~A because it is of independent
interest and may be useful in future work, see Section~\ref{fractalbound}.
Throughout this thesis we assume that
the free running solution lies on the global attractor.
Thus, $U$ reflects the long term behavior of the
Lorenz systems and obeys the {\it a priori\/} bounds discussed
above.
Of those bounds we make exclusive use of the spherical bound given 
as Theorem~\ref{Ktheorem} stated below.

The following proof
is essentially the same as the one given in \cite{Doering95a};
however, it is simpler because
we have already translated the $Z$ variable in the formulation 
of the Lorenz system.

\begin{theorem}
\label{Ktheorem} 
Let $U$ be a trajectory with 
$U_0\in \mathcal{A}$ and assume that $b\ge 2$ and $\sigma$ $r>0$. 
Then $|U(t)|^2 \leq K$ for all $t\in\textbf{R}$ where
\begin{equation}\label{Keqn}
    K = \frac{b^2(r+\sigma)^2}{4(b-1)}
\approx 1540.27.
\end{equation}
\end{theorem}
\begin{proof}
We define a Lyapunov function as
\begin{equation}\label{boundsEqn}
    K = \{(X,Y,Z) \ \vert \ X^2 + Y^2 + Z^2 \le R^2\}
\end{equation}
and consider the evolution of the sphere as determined by the Lorenz equations:
$$
{1\over 2} {dK\over dt} = \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z.\\
$$
$K$ is a decreasing function in time, and so trajectories will move closer to
the point $(0,0,0)$. Solving the constrained maximization problem 
$$
K = \max\{K(X,Y,Z)\ \vert \ \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z \ge 0\}
$$
by using the Lagrange multiplier method with
$$
    f(X,Y,Z,\lambda) = X^2 + Y^2 + Z^2 + \lambda(\sigma X^2 + Y^2 + bZ^2
    +b(r+\sigma)Z)
$$
we may bound the radius of a sphere into which all solutions flow as $t\to
\infty$ where $K_{max} = R^2$.
\end{proof}

\section{The Coupling Method}

%We are interested in a dynamical system formed by two near identical
%subsystems:  one subsystem evolves freely and
%drives the evolution of the other. 
In \cite{Olson14} Azouani, Olson, Titi 
introduced equation~(\ref{noerra}) as a simple
data-assimilation method that constructs an
approximating solution $u$ from partial observations
of an exact solution $U$ over time.
A numerical study of this algorithm was performed by
Gesho \cite{GeshoThesis}, see also Gesho, Olson and Titi \cite{Gesho16}.
The effects of noisy measurements were treated by
Bessaih, Olson and Titi in \cite{Bessaih15}, which led
to a stochastic version of equation~(\ref{noerra}) that
included a $Q$-Brownian motion on the right hand side
to represent measurement errors.
In those works the model problem was the two-dimensional
incompressible Navier--Stokes equations and ${\cal R}(U)$
represented nodal 
measurements of an Eulerian velocity field as might be taken 
by an array of idealized weathervane anemometers that can
measure the exact velocity at a discrete set of points in 
space at any point in time.

Synchronization of coupled copies of the Lorenz system
was first observed by Pecora and Carroll in \cite{Pecora90}.
The Lorenz system was considered in the context of data assimilation 
by Hayden \cite{HaydenThesis} and by Hayden, Olson and Titi 
\cite{Hayden11} and to understand the effects noise
in the observational measurements by Law, Shukla and Stuart 
in \cite{Stuart14}.
This thesis explores the case in which the
available information about the true state of $U$ is 
further contaminated
by a moving time average with an averaging window 
of size $\delta$.
This type of moving average is physically relevant to 
real-world scientific instrumentation that approximates,
for example, the measurement of velocity at any instant
in time by
an average velocity taken over a very small time interval.

Another physically relevant property of most instrumentation is 
that measurements are produced at a sequence of discrete moments 
in time rather than continuously in time.
Sequences of discrete-in-time observations for the Lorenz system
have been considered by Hayden \cite{HaydenThesis},
by Hayden, Olson and Titi in \cite{Hayden11} and 
by Cecilia, Jolly, Foias and Titi in \cite{Cecilia}.
In order to focus on time averages we do not treat
discrete-in-time data in the present thesis.

We now describe the observational measurements of $U$
denoted by $\widetilde{\cal R}(U)$.
Coupling through either the $X$ or $Y$ variable can lead to 
synchronization in the Lorenz system, see \cite{HaydenThesis}.
In this thesis the coupling is on $X$ because the analysis is 
easier and more closely 
represents the analysis used when treating the synchronization
of dynamics given by partial differential equations.
Let 
$\widetilde {\cal R}\colon \R^3\to \R^3$ in equation~(\ref{noerra}) be given 
by one of
$$
R=\cL\circ \cO,\quad
\widetilde R=\cL\circ \widetilde \cO
,\quad
R_{\hat\delta}=\cL\circ \cO_{\hat\delta}
\words{or}
\widetilde R_{\hat\delta}=\cL\circ \widetilde \cO_{\hat\delta},
$$ 
where $\cO$, $\widetilde\cO$, $\cO_{\hat\delta}$ and 
$\widetilde\cO_{\hat\delta}$
represent 
observations with and without noise/time-averages
and
$\cL$
represents an interpolation of the observations 
back into the phase space.
Note that $\hat\delta$ is the size of the averaging window
present in the observational measurements of $U$.
Specifically, we take $\cO\colon \R^3 \rightarrow \R$
and $\cL\colon\R\to\R^3$ 
to be given by 
\begin{equation}\label{Lobserve}
\cO(X,Y,Z)=X\wwords{and} \cL(X)=(X,0,0)
\end{equation}
throughout our study.
Thus, $\cL(U)$ represents exact observations 
of $U$ obtained instantaneously at the time $t$ 
and $\widetilde\cO(U)$ a noisy version of $\cO(U)$ 
which, following \cite{Bessaih15}, satisfies
\begin{equation}\label{tildecO}
\widetilde\cO(U)dt
	=\cO(U)dt+\epsilon dW_t
\end{equation}
where $W_t$ is a standard one-dimensional Brownian motion
with underlying probability space $\Omega$.
The corresponding noise-free and noisy moving time averages
are then given 
by 
\begin{equation}\label{cOdelta}\cO_{\hat\delta}(U)
	={1\over\hat\delta}\int_{t-\hat\delta}^t \cO(U(s))\,ds
\end{equation}
and
\begin{equation}\label{tildecOdelta}
\widetilde\cO_{\hat\delta}(U)
	={1\over\hat\delta}\int_{t-\hat\delta}^t \widetilde\cO(U(s))\,ds.
\end{equation}
%Note that $\delta>0$ above represents the size of the
%averaging window.
For notational convenience we define 
$\cO_0=\cO$ and $R_0=R$ so that $\hat\delta=0$ indicates measurements 
for which the averaging is zero.

As the noise is unknown, the possible choices for ${\cal R}$
used in the feedback control ${\cal R}(u)$ can not include
noise.
This ensures the evolution of the driven solution is given
only in terms of things which are observable.
It may also happen that the size of the averaging present in 
the observations is also unknown. 
In this case, we let $\delta$ represent the time 
averaging in the feedback control.
Thus,
the possible choices for ${\cal R}$ are given given by 
one of $R$ or $R_{\delta}$ where $\delta$ is an approximation
of $\hat\delta$.

When the observations
%are given by $\cO_\delta$ they
are noise-free and $\delta=\hat\delta$ we obtain conditions 
under which $\|U-u\|\to 0$ as $t\to\infty$.
When the observations 
%are given by $\widetilde \cO_\delta$ they
are noisy
$u$ becomes a stochastic process.
In particular, $u$ solves a stochastic differential equation 
when $\hat\delta=0$ and a 
random differential equation when $\hat\delta>0$.
In this case we obtain
bounds of the form
\begin{equation}\label{B1bound}
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big]< B_1.
\end{equation}
Chebyshev's inequality applied to the bound (\ref{B1bound}) implies 
there exists $T>0$ such that
\begin{equation}\label{cheby}
	{\bf P}\big\{ \|U-u\|^2\le B_2\varepsilon^2\big\} \ge 1-B_1/B_2
\end{equation}
for every $B_2>B_1$ and $t>T$.
Thus, the error has a 90 
percent chance of being bounded by $B_2=10B_1$ at any fixed
point in time.

We also consider the general case when 
$\delta\ne\hat\delta$, that is, when the time averaging present 
in the observations is unknown.  
In this case, the equation for $u$ becomes
\begin{equation}\label{NLTAUnkSoln}
    \frac{du}{dt} = \cF(u) -
    \mu \big(\widetilde R_{\hat\delta}(U)
    - {R}_{\delta}
    (u)\big),
\end{equation}
In the absence of noise $\varepsilon=0$ and we 
obtain as Proposition \ref{UKNLTAprop}
conditions and a bound
$B_3$ such that
\begin{equation}\label{lessdeltadelta}
	\limsup_{t\to\infty} \|U-u\|^2 < B_3 (\hat\delta-\delta)^2.
\end{equation}
This analysis suggests it may is possible to recover 
$\hat\delta$ using successively better guesses.
When there is noise we obtain our final
result Proposition~\ref{UKNTAprop} which provides
bounds $B_4$ and $B_5$ such that
\begin{equation}\label{noisydeltadelta}
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] 
		< B_4 (\hat\delta-\delta)^2 + B_5\varepsilon^2.
\end{equation}
In this case, $\delta$ can be tuned to 
match $\hat\delta$ only up to the point 
where the second term starts to dominate the bound.

\chapter{Preliminaries}

In this chapter we prove a local existence theorem 
which will be used later to show our data assimilation 
equations are globally well posed as well as an
integro-Gronwall inequality which will be used to
estimate the accuracy of the synchronization.

We now turn our attention to proving existence and
uniqueness of solutions for the integro-differential equations
which define the driven system as a result of the time averages
present in the observational measurements.
Let
$$
	f\colon [0,\infty)\times\R^n\to\R^n \
	\text{ and }\
 g\colon [0,\infty)\times\R^n\to\R^n$$
be continuous in the first variable and
uniformly Lipschitz in the second.
Consider the integro-differential equation
\begin{equation}\label{intdiff}
     V'=\begin{cases}
{\smallskip}
f\big(t, V\big) & \text { for } t<\delta\\\\
        f\big(t, V\big)
    +\displaystyle {1\over\delta}\int_{t-\delta}^t g\big(s, V(s)\big)\,ds &
    \text{ for } t>\delta\end{cases}
\end{equation}
where $ V\in\R^n$ is a continuous function.
Note that $ V'$ may not be defined at time $t=\delta$, 
unless
$$
	\int_0^\delta g(s,y(s))\,ds\ne 0.
$$
As this is not in general true, then we consider as solutions
to equations (\ref{intdiff}) continuous functions which are piecewise
differentiable.
This equation, similar to the
Volterra equations studied by Levin in \cite{Levin64},
is locally well posed as shown by 
\begin{lemma}\label{localexist}
Suppose $ V\colon [0,T]\to \R^n$ satisfies equations (\ref{intdiff}),
then there exists $\Delta t>0$ such that $ V$ can be uniquely extended to a function
on $[0,T+\Delta t]$ which also satisfies equations (\ref{intdiff}).
\end{lemma}

\begin{proof}
If $T<\delta$, standard existence and uniqueness results
for ordinary differential equations show there exists $\Delta t>0$ 
such that the solution $ V$ can be extended to the interval $[0,T+\Delta t)$.
If $T\ge\delta$, the result follows from a straight-forward 
fixed point argument which we include here for completeness.

Define 
$$D=\max\big\{\, \| V(t)\| : t\in[0,T]\,\big\}+1$$
and
$$M_f=\max\big\{\, \|f(t,v)\| : t\in[0,T+1]\hbox{ and }\|v\|\le D\,\big\}.$$
Let $\gamma_f$ be the Lipschitz constant such that
$$
	\big\|f(t,v_1)-f(t,v_2)\big\|\le \gamma_f \|v_1-v_2\|
\words{for} \|v_1\|,\|v_2\|\le D.
$$
Corresponding to the function $g$
similarly define $M_g$ and $\gamma_g$.
Let
\begin{equation}\label{sizeofh}
	\Delta t=\min\bigg(1,{1\over M_f+M_g},{1\over 2(\gamma_f+\gamma_g)}\bigg).
\end{equation}
and define
\begin{align}
    {\cal X}=\Bigg\{
        v\in {\cal C}([0,T+\Delta t],\R^n):
        \begin{matrix}v(t)=V(t)\hbox{ for }t\le T,\hbox{ and }\hfill\\
        \|v(t)\| \le D\hbox{ for }t\in[T,T+\Delta t]\end{matrix}\,\Bigg\}.
\end{align}
Consider the mapping ${\cal J}\colon{\cal X}\to {\cal C}([0,T+\Delta t],\R^n)$ 
given when $t\le T$ by ${\cal J}(v)(t)= V(t)$ and when $t> T$ by
$$
	{\cal J}(v)(t)= V(T)+\int_T^t f\big(\tau,v(\tau)\big)\,d\tau
		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau g(s,v(s))\,ds\,d\tau.
$$
We claim that ${\cal J}\colon{\cal X}\to{\cal X}$ and
that ${\cal J}$ is a contraction.
Estimate
\begin{align*}
	\|{\cal J}(v)(t)\|
	&
	\le \| V(T)\|+
	\int_T^t \|f\big(\tau,v(\tau)\big)\|\,d\tau\\
	&\phantom{{}\le \| V(T)\|}
		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
			\|g(s,v(s))\|\,ds\,d\tau\\
	&\le (D-1) + \Delta t M_f +\Delta t M_g \le D.
        \end{align*}
Therefore, ${\cal J}\colon{\cal X}\to{\cal X}$.  Moreover,
\begin{align*}
	\|{\cal J}(v_1)(t)&-{\cal J}(v_2)(t)\|
		\le
	\int_T^t \|f\big(\tau,v_1(\tau)\big)-f(\tau,v_2(\tau)\|\,d\tau\\
		&
\phantom{{}-{\cal J}(v_2)(t)\|}
+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
			\|g(s,v_1(s))-g(s,v_2(s))\|\,ds\,d\tau\\
	&\le \Delta t(\gamma_f+\gamma_g) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}\\
	&\le (1/2) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}
        \end{align*}
shows that ${\cal J}$ is a contraction.
Now, by the contraction mapping theorem, there is a unique fixed point
$v\in {\cal X}$ such that ${\cal J}(v)=v$.  
Since this fixed point clearly satisfies equations (\ref{intdiff}),
the lemma is proved.
\end{proof}

We now prove the following integro-differential Gronwall inequality.

>>>>

%\documentclass[journal,comsoc]{IEEEtran}
\documentclass[sigconf, anonymous]{acmart}
%\documentclass[12pt]{article}

\usepackage{algorithmicx}
\usepackage{algorithm,algpseudocode}
\usepackage[english]{babel}
\usepackage{amsmath}

\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{arrows,shapes}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\newcommand{\g}{\sigma}
\newcommand{\s}{\nu}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\iffalse

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{sublemma}{Lemma}[lemma]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\headsep25pt\headheight20pt
\setcounter{secnumdepth}{4}
\pagestyle{fancyplain}
\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
\cfoot{\ \hfill\tiny\sl Draft printed on \today}
\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables

\fi
 %\iffalse
%---------------ACM CCS---------------------%
\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{}
%\fancyhead[C]{Anonymous submission \#837 to ACM CCS 2018} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[]
%\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
%and Communications Security}{Due 8 May 2018}{Dallas, Texas}
\acmYear{2019}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
%-------------------------------------------%
%\fi

\begin{document}
%\begin{multicols}{2}
\title{Progressive Second Price Auction Mechanism for Data-Exchange Models}

@@

%Verizon and At\&T, two major Internet service providers (ISPs), are offering
%shared data plans, where multiple users may purchase and share a single pool of
%data. 
We propose a distributed, privacy-preserving auction-based approach to
allocation in a secondary market for wireless data exchange.
The secondary market is modeled as a fully connected, pure ``point of sale"
market, with initial public platform provided by its parent wireless internet service
provider (ISP). 
The progressive second price (PSP) auction rules provide our underlying auction
structure, allowing for a single degree of freedom, the reserve
price. We suggest that data exchange markets allow for greater flexibility in
mechanism design.
We propose new, natural degrees of freedom, and derive modifiers
to represent the deformation of the strategy space.

Wireless users are modeled as a fixed type with dynamic incentives. Using a game
theoretic analysis, we derive strategy profiles for wireless users
based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
We examine mutations in the strategy space resulting from the new modifiers, and
prove that the desired PSP properties hold. 
Convergence is determined by set theory; we prove that the symmetry of our
strategy space provides built-in conditions for convergence and stability, finally arriving at a network Nash equilibrium.

Trust and privacy issues in secondary markets have yet to be addressed.
As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
In a centrally moderated secondary market, an unregulated,
rational ISP will prevent its secondary market from acting as a competitor.
Competition is desired as it provides incentive for the ISP to protect
and care for its end users.
The distributed nature of PSP extends individual privacy to the secondary market,
allowing for it to compete with its parent ISP. 
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986.10002987</concept_id>
<concept_desc>Security and privacy~Trust frameworks</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003006.10003013</concept_id>
<concept_desc>Security and privacy~Distributed systems security</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003014.10003017</concept_id>
<concept_desc>Security and privacy~Mobile and wireless security</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

%\ccsdesc[500]{Security and privacy~Trust frameworks}
%\ccsdesc[300]{Security and privacy~Distributed systems security}
%\ccsdesc[100]{Security and privacy~Mobile and wireless security}

\keywords{game theory, second price auctions, mobile share, software-defined networks} 
\maketitle

\input{body_acm}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper_acm}
